SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2019-04-02 back.tex
made 'd' lower case

\noindent \textbf{Confidence Tracking}: As shown in
Figure~\ref{fig:spp_structure}, the Pattern Table keeps a count of
hits to each signature through a counter C\textsubscript{sig}. The
number of hits for a given delta per signature are tracked using a
counter C\textsubscript{delta}.  The confidence for a given delta is
approximated through C\textsubscript{d} = C\textsubscript{delta} /
C\textsubscript{sig}.  When SPP enters into a lookahead mode, the path
confidence P\textsubscript{d} is given as:
$$P\textsubscript{d} \;=\; \alpha  \;.\;  C\textsubscript{d}  \;.\;
P\textsubscript{d-1}$$ Here $\alpha$ represents the global accuracy,
calculated as the ratio of the number of prefetches which led to a
demand hit to the number of prefetches recommended in total. The range
of $\alpha$ is [0,1].  $D$ is the lookahead depth. For $d = 1$, when
SPP is in non-speculative mode, P\textsubscript{0} can be thought of
as 1.  The final P\textsubscript{d} is thresholded against prefetch
threshold (T\textsubscript{p}) to reject the low confidence
suggestions and then against a numerically bigger fill threshold
(T\textsubscript{f}) to decide whether to send the prefetch to
L2 Cache (high confidence prefetch) or Last Level Cache (low
confidence prefetch). The two thresholds were empirically set to 25
and 90 respectively, on the scale of 0 to 100.

@@

Moreover, the on-line confidence mechanism used by most prefetchers is
very rudimentary. For example, SPP's internal confidence mechanism is
based on taking the ratio C\textsubscript{d} = C\textsubscript{delta}
/ C\textsubscript{sig}. This confidence was used to make the decision
of whether to prefetch or not to prefetch; and which level to
prefetch.  While this approximation was shown to work in the original
implementation, we believe that a better form of generalized on-line
decision making was possible. Hence, it was necessary to build a
robust and adaptable learning mechanism to accept / reject the
prefetch suggestions; and to decide the fill level (L2 Cache vs Last
Level Cache). Thus, we introduce an independent on-line perceptron
based filtering mechanism.

>>>>

\noindent \textbf{Confidence Tracking}: As shown in
Figure~\ref{fig:spp_structure}, the Pattern Table keeps a count of
hits to each signature through a counter C\textsubscript{sig}. The
number of hits for a given delta per signature are tracked using a
counter C\textsubscript{delta}.  The confidence for a given delta is
approximated through C\textsubscript{d} = C\textsubscript{delta} /
C\textsubscript{sig}.  When SPP enters into a lookahead mode, the path
confidence P\textsubscript{d} is given as:
$$P\textsubscript{d} \;=\; \alpha  \;.\;  C\textsubscript{d}  \;.\;
P\textsubscript{d-1}$$ Here $\alpha$ represents the global accuracy,
calculated as the ratio of the number of prefetches which led to a
demand hit to the number of prefetches recommended in total. The range
of $\alpha$ is [0,1].  The lookahead depth is represented by $d. For $d = 1$, when
SPP is in non-speculative mode, P\textsubscript{0} can be thought of
as 1.  The final P\textsubscript{d} is thresholded against prefetch
threshold (T\textsubscript{p}) to reject the low confidence
suggestions and then against a numerically bigger fill threshold
(T\textsubscript{f}) to decide whether to send the prefetch to
L2 Cache (high confidence prefetch) or Last Level Cache (low
confidence prefetch). The two thresholds were empirically set to 25
and 90 respectively, on the scale of 0 to 100.

@@

Moreover, the on-line confidence mechanism used by most prefetchers is
very rudimentary. For example, SPP's internal confidence mechanism is
based on taking the ratio C\textsubscript{d} = C\textsubscript{delta}
/ C\textsubscript{sig}. This confidence was used to make the decision
of whether to prefetch or not to prefetch; and which level to
prefetch.  While this approximation was shown to work in the original
implementation, we believe that a better form of generalized on-line
decision making is possible. Hence, it was necessary to build a
robust and adaptable learning mechanism to accept / reject the
prefetch suggestions, and to decide the fill level (L2 Cache vs Last
Level Cache). Thus, we introduce an independent on-line perceptron
based filtering mechanism.
